14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-05-18 rules/rules19.tex
Fixed a missing space
Update rules

\header{Result.}
The result of a solver is considered \emph{erroneous} if the response to the
\akey{check-sat} command is \texttt{sat}, or if the returned
unsatisfiable core is not well-formed (e.g., contains names of
formulas that have not been asserted before), or if the returned
unsatisfiable core is not, in fact, unsatisfiable.
Note that an \texttt{unsat} response to \akey{check-sat} but no response to
\akey{get-model} is considered as a special case of the last case
(the empty formula is satisfiable).

@@

\header{Validation.}
In order to check that the model satisfies the benchmark, the organizers will
use the model validating tool available at
{\url{https://github.com/SMT-COMP/postprocessors/tree/master/model-validation-track}}.
It expects as model input a file with the answer to the \akey{check-sat}
command followed by the solver response to the \akey{get-model} command.
The model validator tool will output 
\begin{enumerate}
  \item VALID\hskip .5em for a \texttt{sat} solver response
        followed by a full satisfying model;
  \item INVALID\hskip .5em for
    \begin{itemize}[noitemsep,topsep=0pt]
      \item an \texttt{unsat} solver response to \akey{check-sat},
      \item a \texttt{sat} response to \akey{check-sat} without a response to
        \akey{get-model},
      \item partial models,
      \item malformed models,
      \item models that do not satisfy the input problem; and
    \end{itemize}
  \item UNKNOWN\hskip .5em for
    \begin{itemize}[noitemsep,topsep=0pt]
      \item no solver output (no response to both commands),
      \item an \texttt{unknown} response to \akey{check-sat}.
    \end{itemize}
\end{enumerate}

@@

\subsubsection{\ucoretrack}
  For the \ucoretrack, the error score $e$ and the correctly solved score $n$
  are defined as
  \begin{itemize}
  \item $e=0$ and $n=0$ if the solver
    \begin{itemize}[noitemsep,nolistsep]
      \item aborts without a response to \akey{check-sat}, or
      \item the result of the \akey{check-sat} command is \texttt{unknown},
    \end{itemize}
  \item $e=1$and  $n=0$ if the result is erroneous according to
    Section~\ref{sec:exec:unsat-core},
  \item otherwise, $e=0$ and $n$ is the \emph{reduction} in the number of
    formulas, i.e., $n = N$ minus the number of formula names in the
    reported unsatisfiable core.
  \end{itemize}

>>>>

\header{Result.}
The result of a solver is considered \emph{erroneous} if (i) the
response to the \akey{check-sat} command is \texttt{sat}, (ii) the
returned unsatisfiable core is not well-formed (e.g., contains names of
formulas that have not been asserted before), or (iii) the returned
unsatisfiable core is not, in fact, unsatisfiable.
%
If the solver replies \texttt{unsat} to \akey{check-sat} but gives no
response to \akey{get-model}, this is considered as no reduction, i.e.,
as if the solver would have returned the entire benchmark as an unsat
core.

@@

\header{Validation.}
In order to check that the model satisfies the benchmark, the organizers will
use the model validating tool available at
{\url{https://github.com/SMT-COMP/postprocessors/tree/master/model-validation-track}}.
It expects as model input a file with the answer to the \akey{check-sat}
command followed by the solver response to the \akey{get-model} command.
The model validator tool will output 
\begin{enumerate}
  \item VALID\hskip .5em for a \texttt{sat} solver response
        followed by a full satisfying model;
  \item INVALID\hskip .5em for
    \begin{itemize}[noitemsep,topsep=0pt]
      \item an \texttt{unsat} solver response to \akey{check-sat},
      \item partial models,
      \item malformed models (except if this due to reaching the time limit
        while printing),
      \item models that do not satisfy the input problem; and
    \end{itemize}
  \item UNKNOWN\hskip .5em for
    \begin{itemize}[noitemsep,topsep=0pt]
      \item no solver output (no response to either both commands or
        \akey{get-model}),
      \item an \texttt{unknown} response to \akey{check-sat}.
    \end{itemize}
\end{enumerate}

@@

\subsubsection{\ucoretrack}
  For the \ucoretrack, the error score $e$ and the correctly solved score $n$
  are defined as
  \begin{itemize}
  \item $e=0$ and $n=0$ if the solver
    \begin{itemize}[noitemsep,nolistsep]
      \item aborts without a response to \akey{check-sat}, or
      \item the result of the \akey{check-sat} command is \texttt{unknown},
    \end{itemize}
  \item $e=1$ and  $n=0$ if the result is erroneous according to
    Section~\ref{sec:exec:unsat-core},
  \item otherwise, $e=0$ and $n$ is the \emph{reduction} in the number of
    formulas, i.e., $n = N$ minus the number of formula names in the
    reported unsatisfiable core.
  \end{itemize}
